The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-09 paper/ms.tex
Three peak section

\subsection{Off-Centered emission}

\begin{figure}
  \includegraphics[scale=0.35]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (where the reader is) 
    and the observer is along the $\hat{\j}$ direction. 
    \label{fig:OCspheres}} 
\end{figure}

@@

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5$R and can
have to possible centers positions $C$ along the $\hat{\j}$ direction:
$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
away from the observer and the sphere centered on $+C\hat{\j}$ moves
towards the observer. We consider two values for $C=(0.25,0.50)R$.

@@

In the off-centre emission the variations in the $\mu$ distribution
$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
 $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
$\tau$??). This implies a strong dependence of the observed flux on
the relative position of an observer.  In contrast,the central and
homogeneous source distributions only show a weak anisotropy at the level of
$\Delta\mu\leq 3\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer ($\vert \mu \vert > 0.9$ $\&$ $\vert \mu \vert < 1.0]$). The most
interesting effect is that emission in  some models ($\tau =
10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
presents three peaks (blue-shifted,centred, red-shifted). However, we
do not find any asymmetry in the line produced by the off-center
emission. As in the homogeneous / central model the line gets broader
as the rotational velocity increases.

The results for the off-centred spheres placed closer to the centre
at $C=\pm 0.25R$ do not display such a stronger features discussed above for the
spheres at $C=\pm0.5R$, there is only one model which slightly shows a 
three peak morphology with $\mathrm{V=300km s^{1}}$ and $\tau = 10^{7}$.

@@

\subsection{Three-Peak Profiles}

\begin{figure*}
\includegraphics[scale=0.3]{3peaks.png}
\caption{Three-Peak profiles for the off-center positions. 
   \label{fig:3p_profiles}} 
\end{figure*}

As mentioned in Sec 3.4 Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in Sec 3.4. We select spheres at $C=\pm 0.25, 0.5, 0.75$ for all the 
models, for those who present signs of three peak profiles such as $(V_{max}=50kms^{1} 
\& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), (V_{max}=200kms^{1}
\& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ with the aim 
of get a stronger profile.

Fig. \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
a relation between optical depth, rotational velocity and $C$ must be accomplish.
In particular we found that for the outer spheres $C=\pm 0.75$ the three
peak arise for all of our models with $\tau_{\gamma}=10^{6}$. The main effect of
the rotational velocity is to give rise to the central peak. If the rotational velocity is 
high also the optical depth have to be high in order to compensate the height of the wings 
of the line with the central peak.

Finally we take into account the finite spectral resolution to see if three peaks 
profiles produced by rotation could be observed. Fig.\ref{fig:3p_res} show that even
with a low resolution a three-peak profile would be observed.

>>>>

\subsection{Off-Centered emission}
\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.35]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centered emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (where the reader is) 
    and the observer is along the $\hat{\j}$ direction. 
    \label{fig:OCspheres}} 
\end{figure}

@@

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5$R and can
have two possible centers positions $C$ along the $\hat{\j}$ direction:
$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
away from the observer and the sphere centered on $+C\hat{\j}$ moves
towards the observer. We consider $C=0.5 R$.

@@

In the off-center emission the variations in the $\mu$ distribution
$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
 $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
$\tau$??). This implies a strong dependence of the observed flux on
the relative position of an observer.  In contrast,the central and
homogeneous source distributions only show a weak anisotropy at the level of
$\Delta\mu\leq 3\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer ($\vert \mu \vert > 
0.9$ $\&$ $\vert \mu \vert < 1.0]$).  We do not find any asymmetry in 
the line produced by the off-center emission, The difference
 between the profiles corresponding to the spheres located at $C=-0.5R$ 
 and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
central model the line gets broader as the rotational velocity also 
the central part of the line becomes predominant . 
There is also a signature of possible three peaks profiles for  some models ($\tau = 10^6,
V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
in detail in the Sec.\ref{sec:3p}

@@

\subsection{Three-Peak Profiles}
\label{sec:3p}
\begin{figure*}
\includegraphics[scale=0.3]{3peaks.png}
\caption{Three-Peak profiles for the off-center positions. 
   \label{fig:3p_profiles}} 
\end{figure*}

As mentioned in Sec\ref{sec:off-center} Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in that section. We select spheres at $C=\pm 0.25R, 0.5R, 0.75R$ with a radii of
$0.25R$ for all the models, for those who present signs of three peak profiles such as 
$(V_{max}=50kms^{1} \& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), 
(V_{max}=200kms^{1} \& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
with the aim of get a stronger profile.

Fig. \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
a relation between optical depth, rotational velocity and $C$ must be accomplish.
In particular we found that for the outer spheres $C=\pm 0.75$ the three
peak arises for all of our models with $\tau_{\gamma}=10^{6}$ this is due to 
the fact that the wings of the line move away from the central part as $C$ increase. 
Another requirement is that a high optical must be balanced with a high velocity 
in order to make the wings and the central peak similar in 
height.

Fig.\ref{fig:3p_res} show that even with a low resolution a three-peak profile 
would be observed, this is important for observational porpoises due to the finite 
spectral resolution.
